### 2013-12-02 proposal/proposal/chapter2.tex
fixes

        Cooperative game is a branch of game theory that studies
        strategies of self-interested entities or agents in a setting
        where those agents can increase their payoff by binding agreements
        and cooperating in groups. We let $N$ be a set of players. Any
        subset $S$ of $N$ can form a group called $coalition$. A
        \emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
        a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
        coalition to a real number $v(S)$, the worth of $S$. This number
        usually represents the output or payoff or again the performance
        of these players working together as coalition.  If a coalition
        $S$ is formed, then it can divide its worth, $v(S)$ in any
        possible way among its members. The payoff vector $x \in
        \mathbb{R}^S$ is the amount of payoff being distributed among the
        members of the coalition $S$. The payoff vector satisfies two
        conditions:

        \begin{itemize}
            \item $x_i \geq 0$ for all $i \in N$, and
            \item $\sum_{i \in S} x_i \leq v(S)$
        \end{itemize}

@@

            \emph{Shapley value} is a unique and fair solution concept for
            payoff distribution among the members of the coalition. It
            basically rewards members with the amount of marginal contribution
            they have to the coalition.

@@

            \begin{example}\label{ex:simplecorealpha}
                Consider a game $G = (N, v)$,  where $N = {1,2,3}$ and $v(\{i\}) = 0$, $v(\{Ci\}) = \alpha for |C| = 2$ and $v(\{N\}) = 1$. The $core$ of the game, 
            \end{example}

>>>>

        Cooperative game is a branch of game theory that studies
        strategies of self-interested entities or agents in a setting
        where those agents can increase their payoff by binding agreements
        and cooperating in groups. We let $N$ be a set of players which can form a group called a $coalition$. A
        \emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
        a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
        coalition to a real number $v(N)$, the worth of $N$. This number
        usually represents the output or payoff or again the performance
        of these players working together as coalition.  If a coalition
        $S$ is formed, then it can divide its worth, $v(N)$ in any
        possible way among its members. The payoff vector $x \in
        \mathbb{R}^N$ is the amount of payoff being distributed among the
        members of the coalition $N$. The payoff vector satisfies two
        conditions:

        \begin{itemize}
            \item $x_i \geq 0$ for all $i \in N$, and
            \item $\sum_{i \in N} x_i \leq v(N)$
        \end{itemize}

@@

            \emph{Shapley value} is a unique and fair solution concept for
            payoff distribution among the members of the coalition. It
            basically rewards members with the amount of marginal contribution
            they have to the coalition.  It checks the contribution of member $i$ by adding the agent, to all possible subsets
            of coalitions $S$, where $S \subseteq N\backslash\left\{i\right\}$. If he is added to the set $S$, his
            contribution to the coalition is $v(S \cup \left\{i\right\}) - v(S)$. Average marginal contribution of agent $i$'s
            is calculated by averaging this value over all possible subsets of $N$, in $Shapley value$ equation (\ref{eq:shapley}).

@@

            \begin{example}\label{ex:simplecorealpha}
                In this example, we want to analyse games under conditions which core can be empty. Consider a game $G = (N, v)$,  where $N = {1,2,3}$ and $v(\{i\}) = 0$, $v(\{Ci\}) = \alpha for |C| = 2$ and $v(\{N\}) = 1$. The $(x_1,x_2,x_3)$ distribution vector is in $core$ if $x \geq 0$, $\forall i, \forall j, x_i + x_j \geq \alpha $
            \end{example}

### 2013-12-02 proposal/proposal/chapter3.tex
fixes

It is possible to develop an anytime algorithm by continuing the
verification of this condition against all subsets of size $3$,
$4$, etc. until the algorithm gets interrupted.

@@

In this scenario, we consider multiple communities managed by
multiple master web services, each of which is providing
independent request pools (see Figure \ref{fig_sim2}). Identical
to the first scenario, master web services form coalitions with
web services. We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. As mentioned in Section \ref{sec:coalition}, the used
algorithms \cite{Sandholm:1999:CSG:317145.317152,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
solve key fundamental problems of what coalitions to form, and how
to divide the payoffs among the collaborators.

@@

In this scenario, as new web services are discovered and get ready
to join communities, our algorithm keeps merging and splitting
partitions based on the preference function. The decision to merge
or split is based on the fact that all players must benefit. The
new web services will merge with communities if $all$ the players
are able to improve their individual payoff, and some web services
may split from old communities, if splitting does not decrease the
payoff of any web service of the community. According to
\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
and splitting will converge to a final partition, where web
services cannot improve their payoff. More details of this
algorithm and analysis of generic solutions on coalition formation
games are described in \cite{DBLP:journals/igtr/AptW09}.

\subsection{Taxtation, Subsiding and Community Stability}\label{s:tax}

We discuessed $core$ as one of the preminent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating. Comuunity stability is an attractice property for communities, also communities would benefit by having slightly more web services then having the exact number of web services satisfying task rate cap. One reason is that there is always the possibility that the agents may leave the community or they may under perform from the quality values they were initially performing with.

One way for communities to ensure community stability could be applying a tax, $\epsilon$ ammount of cost for web services changing communities which would make deviation a costly act. However this would require all community coordinators to agree on same ammount of taxtation, being governed by some external entities or web services would join communities with lesser ammount of tax. Another viable solution in our scenario is to stabilize the game using external subsidies. The reason a game is not stable is that the community is not making enough revenue to allocate the players with enough gain. A community master can subside its community with a constant coefficient value of $\lambda$. Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$. Obviously with a big number of $\lambda$ it is always possible to stabilize the community. However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable. Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$ \cite{eps346856} methods.

@@

One of the key criteria reflecting the performance of web service
coalitions is the user satisfaction. User satisfaction can be
measured in terms of quality and quantity of requests (or tasks)
successfully answered by the communities. We initiate the
communities with few web services, then let rejecting and
accepting random web services go for a short number of iterations.
After that, we start the request distribution for the communities
and let them allocate requests among member web services.
Thereafter, we measure the average output performance of tasks in
communities following different methods.

@@

For the \emph{optimal core} method we have used the well known \emph{$\epsilon$-core} method as the
taxtation method to relax the core condition to help communities, attract web services.
We have assigned $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, which allows
subsets of the coalition to gain maximum 15\% of $v(C)$. In the
\emph{optimal $\epsilon$-core} method, we capped the coalition
size to 25 web services, since the method is computationally
intractable as number of web services increase and anything more than that would make it
impractical to run in our simulations. In the other methods, there
were no cap on size of the community and we had communities of
size 60 web services at some points. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and the \emph{3-Way Satisfaction} method, are also performing well.

@@

In Figure \ref{performancemany}, we compare our \emph{Web Services
and many Communities} scenario with a method which ignores QoS
parameters and forms coalitions by allowing web services to join
only if they have enough requests for themselves. In other words,
web services can join a community when the request rate is less
than the throughput of all the member web services. We name this
method \emph{Random Formation} and use it as a benchmark for our
QoS-aware coalition formation process. As the results illustrate,
our method forms better coalitions of web services improving
performance and satisfaction for both web services and coalitions.

>>>>

It is possible to develop an algorithm that continues the
verification of this condition against subsets of size $3$,
$4$, etc. until the algorithm gets interrupted.

@@

In this scenario, we consider multiple communities managed by
multiple master web services, each of which is providing
independent request pools (see Figure \ref{fig_sim2}). Identical
to the first scenario, master web services form coalitions with
web services. We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. As mentioned in Section \ref{sec:coalition}, the used
algorithms in \cite{Sandholm:1999:CSG:317145.317152,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
solve key fundamental problems of what coalitions to form, and how
to divide the payoffs among the collaborators.

@@

In this scenario, as new web services are discovered and get ready
to join communities, our algorithm keeps merging and splitting
partitions based on the preference function. The decision to merge
or split is based on the fact that all players must benefit. The
new web services will merge with communities if $all$ the players
are able to improve their individual payoff, and some web services
may split from old communities, if splitting does not decrease the
payoff of \emph{any} web service of the community. According to
\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
and splitting will converge to a final partition, where web
services cannot improve their payoff. More details of this
algorithm and analysis of generic solutions on coalition formation
games are described in \cite{DBLP:journals/igtr/AptW09}.

\subsection{Taxation, Subsiding and Community Stability}\label{s:tax}

ssed $core$ as one of the prominent solution concepts in cooperative games. Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group. However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal amount of $\epsilon$ by deviating. Stability is an attractive property for communities. In addition, communities would benefit by having slightly more web services then the exact number of web services satisfying task rate cap. This is because  there is always a possibility that the agents may leave the community or they may under perform and degrade the quality values they were initially performing with.

One way for communities to ensure  stability could be  by applying a tax, $\epsilon$ amount of cost for web services changing communities which would make deviation a costly act. However this would require all community coordinators to agree on a same amount of taxation, being governed by some external entities or web services would join communities with lesser amount of tax. Another viable solution to our scenario is to stabilize the game using external subsidies. The reason a gamWe discue is not stable is that the community is not making enough revenue to allocate  enough gain to the players. A community master can subside its community with a constant coefficient value of $\lambda$.

Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$.

Obviously with a big number of $\lambda$, it is always possible to stabilize the community. However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable. Subsiding or taxing in order to reduce the bargaining power of sub coalitions are called $taxation$ \cite{eps346856} methods.

@@

One of the key criteria reflecting the performance of web service
coalitions is the user satisfaction. User satisfaction can be
measured in terms of quality and quantity of requests (or tasks)
successfully answered by the communities. We initiated the
communities with few web services, then let rejecting and
accepting random web services go for a short number of iterations.
After that, we started the request distribution for the communities
and let them allocate requests among member web services.
Thereafter, we measured the average output performance of tasks in
communities following different methods.

@@

For the \emph{optimal core} method we have used the well known \emph{$\epsilon$-core} method as the
taxtation method to relax the core condition to help communities, attract web services.
We have assigned $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, which allows
subsets of the coalition to gain maximum 15\% of $v(C)$. In the
\emph{optimal $\epsilon$-core} method, we capped the coalition
size to 25 web services, since the method is computationally
intractable as number of web services increase and anything more than that would make it
impractical to run in our simulations. In the other methods, there
were no cap on size of the community and we had communities of
size 60 web services at some points. In this scenario our community receives 30 tasks on average per iteration, from users. The community, after the task distribution process on each iteration, will reevaluate QoS metrics of its members and can check for new membership requests. Web services may join or leave the community between iterations. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and the \emph{3-Way Satisfaction} method, are also performing well.

@@

In Figure \ref{performancemany}, we compare our \emph{Web Services
and many Communities} scenario with a method which ignores QoS
parameters and forms coalitions by allowing web services to join
only if they have enough requests for themselves. In other words,
web services can join a community when the request rate is less
than the throughput of all the member web services. We name this
method \emph{Random Formation} and use it as a benchmark for our
QoS-aware coalition formation process. In this scenario, each user individually generates randomly
between 0 to 10 number of tasks per iteration, then the users target a community and direct their requests to the chosen community. As the results illustrate,
our method forms better coalitions of web services improving
performance and satisfaction for both web services and coalitions.
